Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-29 grove-paper.tex
Commit before massive figure fixup

This section introduces collaborative structure editing in Grove.
We begin in \autoref{sub:Program Representation} by covering how we represent expressions with holes as graphs,
\autoref{sub:Single-User Actions} explores edits by a single user, Alice,
and \autoref{sub:Multi-user Edits} explores edits by multiple users, Alice and Bob,
each of whom is editing their own instance of a program.

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\end{tikzpicture}

@@

TODO: Remove subfigure captions
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole.
\autoref{fig:A simple tree with a hole-a}:~User interface.
\autoref{fig:A simple tree with a hole-b}:~Graph representation.}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\columnwidth}
\centering
\caption{}
\label{fig:Construction-a}
TODO: remove this figure
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\columnwidth}
\centering
\caption{}
\label{fig:Construction-b}
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction.
\autoref{fig:Construction-a}:~User interface.
\autoref{fig:Construction-b}:~\autoref{fig:A simple tree with a hole-b} after adding \Vertex{\vidConstructionY} and \Edge{\eidConstructionY}.}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:Change-a}
TODO: delete and leave deleted z8

TODO: delete "x" instead of "y"

\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:Change-b}
TODO: Delete this figure
\newedge{ChangeZ}{R}
\newvertex{ChangeZ}{z}
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vChangeZ" [> "\eChangeZ"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change.
\autoref{fig:Change-a}:~\autoref{fig:Construction-b} after deleting \Edge{\eidConstructionY}.
\autoref{fig:Change-b}:~\autoref{fig:Change-a} after adding \Vertex{\vidChangeZ} and \Edge{\eidChangeZ}.}
\label{fig:Change}
\end{figure}

>>>>

This section introduces collaborative structure editing in Grove.
We begin in \autoref{sub:Program Representation} by covering how we use graphs to represent expressions with holes,
\autoref{sub:Single-User Actions} explores edits by a single user, Alice,
and \autoref{sub:Multi-user Edits} explores edits by multiple users, Alice and Bob,
each of whom is editing their own instance of a program.

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole.
\autoref{fig:A simple tree with a hole-a}:~User interface.
\autoref{fig:A simple tree with a hole-b}:~Graph representation.}
\label{fig:A simple tree with a hole}
\end{figure}

@@

TODO: Remove subfigure captions

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{minipage}[t]{0.49\columnwidth}
\centering
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\end{tikzpicture}
\caption{Construction.
\autoref{fig:Construction-b}:~\autoref{fig:A simple tree with a hole-b} after adding \Vertex{\vidConstructionY} and \Edge{\eidConstructionY}.}
\label{fig:Construction}
\label{fig:Construction-b}
\end{minipage}
%%%%%%%%
\hfill
%%%%%%%%
\begin{minipage}[t]{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   {},
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\path (-1cm,-2.5cm) graph[graph style] {
 "\vSimpleX" % [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\caption{Change.}
\label{fig:Change-a}
\label{fig:Change}
\end{minipage}
%%%%%%%%
\hfill{}
\end{figure}

@@
